### 2019-04-15 paper/paper.tex
updated spearman table
removed reference to the graph

To collect our data for package usage in public projects, 
we turned to the Google BigQuery \code{github\_repos} data 
set\footnote{https://bigquery.cloud.google.com/dataset/bigquery-public-dat:github\_repos}.
From this data, we skimmed all projects and pulled those 
written in JavaScript, resulting in an initial total of 9,017,221 
repositories. Simply being written in JavaScript is not enough to detect
\code{npm} usage, so to find repositories using \code{npm} packages
we looked for projects that contained a \code{package.json} 
file. After confirming that the formatting of the file matched the \code{npm}
standard, we are able to confidently say that any remaining packages are 
using \code{npm} packages. From this criteria, we compiled a list 
of applicable project 
repositories from GitHub.
Using the \code{GitHub} platform API and the list of valid repository names 
from before, we cloned the GitHub repository for a random subset of all projects. With
this, we were then able to determine the date and time of every 
commit of these projects, as well as the list of included \code{npm} packages
at the time of every commit, as listed in every historic version of 
\code{package.json}, providing us with the \code{npm} packages used by that repository
at any given time in the project's history. The results showed that on average a repository 
had 37.9 commits to its \code{package.json}. Ultimately, of the 9,017,221 
public \code{GitHub} projects written in JavaScript and out of all of the repositories
using \code{npm} packages, we selected 40,000 repositories as
a representative data set for the analysis.

@@

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c c c}
     & \code{npm} PageRank & Downloads & \code{GitHub} \\
    \hline
    \code{npm} PageRank & - & 0.389 & 0.405\\
    Downloads & 0.389 & - & 0.576\\
    \code{GitHub} & 0.405 & 0.576 & -\\

@@

To inspect these relationships in greater detail, Figure \ref{corrGraph}
plots the differences between ranks of each metric. It may be observed
that our data presents a relatively normal distribution of differences
between popularity ranks, again matching the findings of the original paper \cite{Wittern:2016}.
From these results, we can conclude that our three metrics of popularity
are measures of different package attributes, and that packages
with a high rank in one metric can be ranked much lower by another metric.

@@

As we demonstrated in section \ref{metricDiff}, packages that perform well
by one measure of popularity often perform poorly by others. The original paper
proposes that one major source of this differential is in the way that packages
are used \cite{Wittern:2016}. It is surmised that packages ranked highly by the
\code{npm} PageRank system are primarily packages that are used often within the
\code{npm} ecosystem, and tend to be \textbf{core utility} packages that are used
as dependencies for other \code{npm} packages, and rarely used outside of the
\code{npm} package environment. Conversely, packages that exhibit
significant popularity by the \code{GitHub} rank tend to be \textbf{end user} packages more
commonly used in application development as opposed to package construction. 
In order to confirm this hypothesis, we examine keywords associated with each
ranking system, as is done in the original paper.
Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
application frameworks, we feel confident confirming the hypothesis of the original authors.

>>>>

To collect our data for package usage in public projects, 
we turned to the Google BigQuery \code{github\_repos} data 
set\footnote{https://bigquery.cloud.google.com/dataset/bigquery-public-dat:github\_repos}.
From this data, we skimmed all projects and pulled those 
written in JavaScript, resulting in an initial total of 9,017,221 
repositories. Simply being written in JavaScript is not enough to detect
\code{npm} usage, so to find repositories using \code{npm} packages
we looked for projects that contained a \code{package.json} 
file. After confirming that the formatting of the file matched the \code{npm}
standard, we are able to confidently say that any remaining packages are 
using \code{npm} packages. From this criteria, we compiled a list 
of applicable project 
repositories from GitHub.
Using the \code{GitHub} platform API and the list of valid repository names 
from before, we cloned the GitHub repository for a random subset of all projects. With
this, we were then able to determine the date and time of every 
commit of these projects, as well as the list of included \code{npm} packages
at the time of every commit, as listed in every historic version of 
\code{package.json}, providing us with the \code{npm} packages used by that repository
at any given time in the project's history. The results showed that on average a repository 
had 37.9 commits to its \code{package.json}, and had 8.85 \code{npm} dependencies as well as 
13.6 \code{devDependencies}. Ultimately, of the 9,017,221 
public \code{GitHub} projects written in JavaScript and out of all of the repositories
using \code{npm} packages, we selected 40,000 repositories as
a representative data set for the analysis.

@@

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c c c}
     & \code{npm} PageRank & Downloads & \code{GitHub} \\
    \hline
    \code{npm} PageRank & - & 0.550 & 0.345\\
    Downloads & 0.550 & - & 0.444\\
    \code{GitHub} & 0.345 & 0.444 & -\\

@@

% To inspect these relationships in greater detail, Figure \ref{corrGraph}
% plots the differences between ranks of each metric. It may be observed
% that our data presents a relatively normal distribution of differences
% between popularity ranks, again matching the findings of the original paper \cite{Wittern:2016}.

From these results, we can say that our data supports the findings of the original paper, and
that our three metrics of popularity
are measures of different package attributes. Functionally, this means that packages
with a high rank in one metric can be ranked much lower by another metric.

@@

As we demonstrated in section \ref{metricDiff}, packages that perform well
by one measure of popularity can perform poorly by others. The original paper
proposes that one major source of this differential is in the way that packages
are used \cite{Wittern:2016}. It is surmised that packages ranked highly by the
\code{npm} PageRank system are primarily packages that are used often within the
\code{npm} ecosystem, and tend to be \textbf{core utility} packages that are used
as dependencies for other \code{npm} packages, and rarely used outside of the
\code{npm} package environment. Conversely, packages that exhibit
significant popularity by the \code{GitHub} rank tend to be \textbf{end user} packages more
commonly used in application development as opposed to package construction. 
In order to confirm this hypothesis, we examine keywords associated with each
ranking system, as is done in the original paper.
Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
application frameworks, we feel confident confirming the hypothesis of the original authors.
